A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-30 manuscript.Rmd
don't use bookdown because automate() does not inference the correct output for base_format
repro now acknowledges more file dependencies
fix dependency structure for temp.bib

@@

  bookdown::markdown_document2:
    base_format: rticles::mdpi_article

@@

   - \usepackage[labelformat=empty]{caption}

@@

```{r, include=FALSE}
knitr::write_bib(
  c(
    .packages(),
    "repro",
    "here",
    "rticles",
    "gert",
    "bookdown",
    "lavaan",
    "knitr",
    "targets",
    "renv",
    "tidyverse"
  ),
  here("packages.bib")
)
cat(c(readLines(here::here("packages.bib")), "\n", readLines(here::here("references.bib"))), sep = "\n", file = "temp.bib")
```

>>>>

  images:
    - images/nutshell.svg
  files:
    - references.bib

@@

  rticles::mdpi_article

@@

@@
